\section{Research Questions}\label{sec:lit_rqs}

With these research questions, we aim to synthesize the current state of \rt research in terms of most frequently used approaches and metrics as well as understand researchers' motivations and efforts regarding the practical implementation of their proposed techniques.

\paragraph{RQ\ref{chap:literature_review}.1: What are the main approaches used for \rt techniques and what are the metrics used to evaluate them?} --- We want to have an overview of the approaches most used in this field, including what information is required from the software, what algorithms are put into use and what goal are they trying to achieve. In addition, we want to know what metrics are widely accepted among researchers to evaluate such approaches and whether there is evidence to suggest that these metrics correlate to the technique's practical applicability.

\paragraph{RQ\ref{chap:literature_review}.2: Is \rea an explicit concern in \rt research?} --- We want to find out if there is a meaningful number of papers that state \rea as their motivation and include it as part of their problem description. Additionally, we want to understand what are the main steps that authors usually take towards addressing these concerns with the tools, techniques and solutions they provide.
    
\paragraph{RQ\ref{chap:literature_review}.3: Is there evidence that techniques developed in academia make their way into software in practice?} --- In an effort to measure the extent of active industry-academia collaborations, we want to highlight examples of techniques that have been put into practice at some point during the development of the work. To provide a clearer picture, we asked authors of the selected studies to provide details of the state of their research post publication.