\section{Threats to Validity}
\label{sec:ind_threats}

\paragraph{Construct validity}
The observations in \Cref{chap:industry} were only possible due to a collaboration with an European technology company, facilitated by a person who is in frequent contact with both the company and the academic world.
It is important to note that the findings relate to an experience of only seven weeks at only one office of the company.
We did our best efforts to understand the internal testing strategies and workflows, but the overall complexity of the processes is too high to be completely comprehended in a short timeframe.

\paragraph{Internal validity} 
The interviews that were conducted for this chapter were based on the research questions presented here.
These research questions were designed to reflect our goals when designing that part of the research, and inevitably narrow the possible findings and guide the general outcome of the study.
The quotes included in this chapter are transcribed from verbal interviews with practitioners and edited by the author for legibility, clarity and cohesiveness with the text.
It is possible that a response was misinterpreted by the interviewer or that the meaning of a quote is not fully clear to a reader.
We took great care of transcribing the interviews as accurately as possible, and of ensuring that their meaning was not altered by cherry-picking quotes or adjusting their wording.
Mitigating this risk, the chapter has been read and approved by two people from the industrial partner, ensuring their point of view is correctly expressed.
Due to a non-disclosure agreement with the industrial partner, we cannot provide the full unedited transcripts of the interviews.

\paragraph{Conclusion validity}
The conclusions drawn from the interviews are a result of our own interpretation of the situation, based on the observed data, on discussions with members of the company, and related information extracted from the software engineering literature.
Inevitably these conclusions are influenced by the background of the researchers who, to the degree of possibility, allowed the newfound information to shape the conclusions, not the opposite.
Unfortunately, this study is not easily replicable, as core components of it are left undisclosed due to confidentiality concerns by the industrial partner. 

\paragraph{External validity}
These observations relate to one team at one office at a large company.
The conclusions we draw relate solely to that team and might not generalize to the practices observed in the rest of the company.
Furthermore, we make no claims that these findings generalize to software industry as a whole.
This threat can only be mitigated if more companies are willing to allow researchers to interview their employees and understand their testing processes and challenges.