\rowmetric{Selection/reduction count/percentage}{}{\citetalias{hirzel_graph-walk-based_2016}, \citetalias{vost_trace-based_2016}, \citetalias{blondeau_test_2017}, \citetalias{bach_coverage-based_2017}, \citetalias{vasic_file-level_2017}, \citetalias{celik_regression_2017}, \citetalias{zhang_hybrid_2018}, \citetalias{yilmaz_case_2018}, \citetalias{celik_regression_2018}, \citetalias{azizi_retest_2018}, \citetalias{fu_resurgence_2019}, \citetalias{eda_efficient_2019}, \citetalias{machalica_predictive_2018}, \citetalias{shi_understanding_2019}, \citetalias{chen_context-aware_2021}, \citetalias{zhang_comparing_2022}, \citetalias{cingil_black-box_2022}}{\citetalias{gotlieb_using_2017}, \citetalias{chi_multi-level_2017}, \citetalias{eda_efficient_2019}, \citetalias{goyal_test_2019}, \citetalias{noemmer_evaluation_2020}}{}{Absolute or relative size of the resulting test suite compared to the original.}
\rowmetric{Average Percentage of Faults Detected (APFD)}{\citetalias{srikanth_requirements_2016}, \citetalias{lu_how_2016}, \citetalias{srikanth_test_2016}, \citetalias{busjaeger_learning_2016}, \citetalias{marijan_effect_2016}, \citetalias{spieker_reinforcement_2017}, \citetalias{ouriques_test_2018}, \citetalias{haghighatkhah_test_2018}, \citetalias{miranda_fast_2018}, \citetalias{chen_optimizing_2018}, \citetalias{yu_terminator_2019}, \citetalias{wu_time_2019}, \citetalias{lima_multi-armed_2022}, \citetalias{peng_empirically_2020}, \citetalias{bagherzadeh_reinforcement_2022}, \citetalias{pan_dynamic_2020}, \citetalias{zhou_parallel_2022}, \citetalias{li_aga_2021}, \citetalias{abdelkarim_tcp-net_2022}, \citetalias{yaraghi_scalable_2022}, \citetalias{omri_learning_2022}, \citetalias{greca_comparing_2022}}{}{}{}{A measure of how quickly a test suite detects faults, on average. Includes many variations, such as APFDc and NAPFD.}
\rowmetric{Testing time}{}{\citetalias{tahvili_dynamic_2016}, \citetalias{ramler_tool_2017}, \citetalias{celik_regression_2017}, \citetalias{garousi_multi-objective_2018}, \citetalias{yilmaz_case_2018}, \citetalias{celik_regression_2018}, \citetalias{zhong_testsage:_2019}, \citetalias{shi_understanding_2019}, \citetalias{mehta_data-driven_2021}, \citetalias{zhang_comparing_2022}, \citetalias{cingil_black-box_2022}}{\citetalias{goyal_test_2019}, \citetalias{philip_fastlane:_2019}, \citetalias{noemmer_evaluation_2020}}{}{Time required to execute the prioritized/selected/reduced test suite as opposed to the original suite.}
\rowmetric{Accuracy/precision/recall}{\citetalias{busjaeger_learning_2016}, \citetalias{kwon_cost-effective_2017}, \citetalias{pan_dynamic_2020}, \citetalias{abdelkarim_tcp-net_2022}, \citetalias{omri_learning_2022}}{\citetalias{blondeau_test_2017}, \citetalias{magalhaes_automatic_2016}, \citetalias{kwon_cost-effective_2017}, \citetalias{guo_decomposing_2019}, \citetalias{machalica_predictive_2018}, \citetalias{xu_requirement-based_2021}}{\citetalias{philip_fastlane:_2019}}{}{Measures of correctness and completeness of the resulting test suite (e.g., count of false positives and false negatives).}
\rowmetric{Fault Detection Capability}{\citetalias{schwartz_cost-effective_2016}, \citetalias{wang_enhancing_2016}, \citetalias{marijan_effect_2016}}{\citetalias{kwon_cost-effective_2017}, \citetalias{zarges_artificial_2021}, \citetalias{chen_context-aware_2021}, \citetalias{cingil_black-box_2022}}{}{}{Number or proportion of faults detected by the resulting suite compared to the original.}
\rowmetric{Fault Detection Rate (FDR)}{\citetalias{aman_application_2016}, \citetalias{strandberg_experience_2016}, \citetalias{yu_terminator_2019}}{\citetalias{azizi_retest_2018}}{}{}{Time to detect faults compared to the optimal RT suite.}
\rowmetric{Coverage Effectiveness (CE)}{\citetalias{noor_similarity-based_2016}, \citetalias{yu_terminator_2019}, \citetalias{magalhaes_hsp_2020}, \citetalias{lubke_selecting_2020}}{\citetalias{magalhaes_hsp_2020}, \citetalias{lubke_selecting_2020}}{}{\citetalias{yoshida_fsx_2016}}{Measure of the tradeoff between cost of the test suite and structural coverage of the SUT.}
\rowmetric{Time/tests To First Failure}{\citetalias{noor_similarity-based_2016}, \citetalias{chen_optimizing_2018}, \citetalias{zhu_test_2018}, \citetalias{lima_multi-armed_2022}, \citetalias{zhou_beating_2020}, \citetalias{pan_dynamic_2020}, \citetalias{zhou_parallel_2022}, \citetalias{greca_comparing_2022}}{\citetalias{blondeau_test_2017}, \citetalias{zarges_artificial_2021}, \citetalias{greca_comparing_2022}}{}{}{Number of tests or amount of time needed to reach the first failure.}
\rowmetric{Fault detection within a budget}{\citetalias{wang_enhancing_2016}, \citetalias{bach_coverage-based_2017}, \citetalias{lima_multi-armed_2022}, \citetalias{greca_comparing_2022}}{\citetalias{pradhan_search-based_2016}, \citetalias{bach_coverage-based_2017}, \citetalias{greca_comparing_2022}}{}{}{Faults still detected when restricting the testing time budget.}
\rowmetric{Cost-benefit model}{\citetalias{schwartz_cost-effective_2016}, \citetalias{tahvili_cost-benefit_2016}}{\citetalias{garousi_multi-objective_2018}, \citetalias{mehta_data-driven_2021}}{}{}{Mathematical models considering costs and benefits of applying a technique throughout development.}
\rowmetric{Fault Detection Loss}{\citetalias{najafi_improving_2019}}{\citetalias{najafi_improving_2019}, \citetalias{chen_multi-objective_2021}}{\citetalias{shi_evaluating_2018}, \citetalias{cruciani_scalable_2019}}{}{Number or proportion of faults undetected by the selected/reduced test suite compared to the original.}
\rowmetric{Comparison to expert}{\citetalias{buchgeher_improving_2016}}{\citetalias{buchgeher_improving_2016}, \citetalias{magalhaes_automatic_2016}}{}{}{Compares the output of the tool with a list of tests selected by the project architect.}
\rowmetric{Faults per tests/time}{\citetalias{kwon_cost-effective_2017}}{\citetalias{kwon_cost-effective_2017}}{}{}{Number of faults deteted per number of tests or testing time.}
\rowmetric{Number of tests added}{}{}{}{\citetalias{yoshida_fsx_2016}}{Number of tests added to the test suite.}
\rowmetric{Algorithm performance measures}{}{\citetalias{pradhan_search-based_2016}}{}{}{Fitness value or hypervolume metrics applied to search-based algorithms}
\rowmetric{Accumulated regression risk}{\citetalias{lubke_selecting_2020}}{\citetalias{lubke_selecting_2020}}{}{}{How much of the "regression risk" is covered by the tests.}
\rowmetric{Rank Percentile Average (RPA)}{\citetalias{bertolino_learning--rank_2020}, \citetalias{bagherzadeh_reinforcement_2022}}{\citetalias{bertolino_learning--rank_2020}}{}{}{Comparison between the predicted ranking and the actual ranking (from the dataset).}
\hiderowcolors
\bottomrule
