\rowapproach{History-based}{\citetalias{srikanth_test_2016}, \citetalias{aman_application_2016}, \citetalias{busjaeger_learning_2016}, \citetalias{strandberg_experience_2016}, \citetalias{marijan_effect_2016}, \citetalias{kwon_cost-effective_2017}, \citetalias{haghighatkhah_test_2018}, \citetalias{yu_terminator_2019}, \citetalias{najafi_improving_2019}}{\citetalias{kwon_cost-effective_2017}, \citetalias{machalica_predictive_2018}, \citetalias{najafi_improving_2019}}{}{}{Uses information from previous testing cycles to decide about test case relevance.}
\rowapproach{Change-based}{\citetalias{strandberg_experience_2016}}{\citetalias{oqvist_extraction-based_2016}, \citetalias{ramler_tool_2017}, \citetalias{vasic_file-level_2017}, \citetalias{celik_regression_2017}, \citetalias{zhang_hybrid_2018}, \citetalias{yilmaz_case_2018}, \citetalias{celik_regression_2018}, \citetalias{guo_decomposing_2019}, \citetalias{fu_resurgence_2019}, \citetalias{eda_efficient_2019}, \citetalias{shi_understanding_2019}, \citetalias{chen_context-aware_2021}, \citetalias{zhang_comparing_2022}, \citetalias{cingil_black-box_2022}, \citetalias{greca_comparing_2022}}{\citetalias{eda_efficient_2019}}{}{Uses changes between versions to identify the relevant test cases.}
\rowapproach{Coverage-based}{\citetalias{busjaeger_learning_2016}, \citetalias{bach_coverage-based_2017}, \citetalias{ouriques_test_2018}, \citetalias{yu_terminator_2019}, \citetalias{magalhaes_hsp_2020}, \citetalias{lubke_selecting_2020}}{\citetalias{ramler_tool_2017}, \citetalias{bach_coverage-based_2017}, \citetalias{zhong_testsage:_2019}, \citetalias{magalhaes_hsp_2020}, \citetalias{lubke_selecting_2020}}{\citetalias{shi_evaluating_2018}, \citetalias{noemmer_evaluation_2020}}{\citetalias{yoshida_fsx_2016}}{Uses structural coverage information, whereby coverage can be of statement, method, class, file, etc.}
\rowapproach{Cost-aware}{\citetalias{lu_how_2016}, \citetalias{wang_enhancing_2016}, \citetalias{tahvili_dynamic_2016}, \citetalias{tahvili_cost-benefit_2016}, \citetalias{yu_terminator_2019}, \citetalias{zhou_parallel_2022}}{\citetalias{tahvili_dynamic_2016}, \citetalias{chen_multi-objective_2021}}{}{}{Utilizes test case cost or time information to assess test relevance.}
\rowapproach{Requirements-based}{\citetalias{srikanth_requirements_2016}}{}{\citetalias{goyal_test_2019}}{}{Relate tests with project-sensitive information, such as requirements and risk assessments.}
\rowapproach{Manual classification}{\citetalias{tahvili_dynamic_2016}, \citetalias{tahvili_cost-benefit_2016}, \citetalias{yu_terminator_2019}}{\citetalias{tahvili_dynamic_2016}}{}{}{Requires at least some information that must be manually inputted by an expert.}
\rowapproach{Model-based}{\citetalias{buchgeher_improving_2016}, \citetalias{ouriques_test_2018}}{\citetalias{buchgeher_improving_2016}}{}{}{Informs the test technique using behavioural or architectural models.}
\rowapproach{Trace-based}{}{\citetalias{vost_trace-based_2016}, \citetalias{zhong_testsage:_2019}}{}{}{Provides inputs and keeps track of the effects of those inputs throughout the program.}
\rowapproach{Fault-based}{\citetalias{marijan_effect_2016}, \citetalias{zhu_test_2018}}{\citetalias{leong_assessing_2019}, \citetalias{chen_multi-objective_2021}, \citetalias{cingil_black-box_2022}}{}{}{Utilizes information related to fault detection or failure beaviour.}
\rowapproach{Test code}{\citetalias{noor_similarity-based_2016}, \citetalias{miranda_fast_2018}, \citetalias{peng_empirically_2020}, \citetalias{greca_comparing_2022}}{}{\citetalias{cruciani_scalable_2019}}{}{Uses the plain text source code of the test cases.}
\rowapproach{Load factor}{\citetalias{buchgeher_improving_2016}}{\citetalias{buchgeher_improving_2016}}{}{}{Indicates what parts of the SUT are most used by different services and components.}
\rowapproach{Author count}{}{\citetalias{leong_assessing_2019}}{}{}{Number of authors associated with a certain part of the SUT.}
\rowapproach{Execution context}{}{\citetalias{celik_regression_2017}, \citetalias{chen_context-aware_2021}}{}{}{Considers environment data such as libraries, APIs, databases, operating system, etc.}
\hiderowcolors
\bottomrule
